A game of competition over risk

### 2023-04-20 paper/article.tex
Updates from Overleaf

We recall \footnote{Our thanks go to \identifier{Jules Pondard} for suggesting to use the well-known discrete version of this theorem.} Theorem 2.1 from \citet{Lotker2008-tx}:

@@

>>>>

We recall Theorem 2.1 from \citet{Lotker2008-tx}:

@@

\section*{Acknowledgement}

We thank \identifier{Aurélie Coursimault}, \identifier{Marc Lanctot}, \identifier{Jules Pondard} and \identifier{Philippe Raimbourg} for helpful discussions and useful comments.
